### 2010-03-16 papers/icfp-2010-desc/paper_idesc.tex
IDesc@ICFP: update outline to accomodate the arrival of Hutton's razor. Includes tagged indexed descriptions.

\begin{structure}
<- Hutton's razor
    ???
\end{structure}

\note{Begging for a transtion here.}

@@

\begin{structure}
<- Hutton's razor is a free monad
    <- What is it?
        -> It's an evaluator
    ???
\end{structure}

>>>>

\begin{structure}
<- Tagged constructor choice
    <- Index available when defining the data-type
        -> Can influence the choice of constructors
        -> Dependently-typed data-types
            <- term (index) influence types
    -> Two parts
        <- Always on the menu
            <- E : EnumU 
            <- ED : E -> IDesc I
        <- Index-dependent
            <- F : I -> EnumU 
            <- FD : (i : I) -> spi (F i) (\_ -> IDesc I)
        -> taggedIDesc I == Sigma E ED x Sigma F FD
        -> toIDesc : (I : Set) -> taggedIDesc I -> (I -> IDesc I)
\end{structure}

\begin{structure}
<- Hutton's razor
    <- Types
        <- 'Nat
        <- 'Bool
    <- Term [figure]
        <- val : Val a -> 'a  for Val : Ty -> Set, mapping to Nat and Bool
        <- cond : 'Bool -> a -> a -> a
        <- plus : 'Nat -> 'Nat -> 'Nat
        <- le : 'Nat -> 'Nat -> 'Bool
    -> evaluation: IMu TermD -> Val
        -> it is a catamorphism
            <- Look closer at the type
        -> implementation [code]
            <- Just define one reduction step
            -> cata does the rest
                /> cata is for free!
    /> Closed term
        <- only constants and operations on them
        -> Extend Val with Var : Ty -> Set, mapping to EnumU
            -> Open term
            -> Language of well-typed terms
                <- By construction
        <- evaluator, with a context
            -> First, close variables
                -> Perform assignment
                <- subst [code]
            /> Then, perform subst everywhere in the term
                -> Show type [code]
                /> This is a bind!?
                -> There is some more structure 
                    -> We should try to get it
\end{structure}

\note{Begging for a transition here.}

@@

\begin{structure}
<- Hutton's razor is a free monad
    <- substI was our candidate bind
        -> Massage the definition of expr to get it for free
    <- Finding the functor
        <- 'val is the return
        <- The other components are the action
        -> Updated tagged description [figure]
    -> Compute the free monad Hutton * X
        -> With X = Val: We get back our closed terms
        -> With X = Val + Var vars: We get back our open terms
    /> On open terms, we get a substitution
        -> Apply substI on assgnmt
            -> Have a well-typed language
            -> Get a safe evaluator 
                <- for well-typed terms 
                <- in well-typed contexts
\end{structure}
